Weather Data Integration and Assimilation System\\

### 2020-02-09 introduction/sec_2-problem_and_objectives.tex
Update problem statement

\section{Problem Statement}
\dbc{Convert following bullets to a paragraph. Goals belongs to next section. What we need here is a set of sentences highlighting the needs that are used to derive goals. Then provide a single sentence problem statement. Look at some of the thesis I shared via OneNote and my website for example problem statements.}
\begin{itemize}
    \item Handling spatio-temporal weather data is challenging
    \item Need an extendable system to support weather models by efficiently storing and retrieving data
    \item Goal is to design and develop a Weather Data Integration and Assimilation System that,
    \begin{itemize}
        \item Integrates weather data from different sources with quality control
        \item Efficiently store spatio-temporal weather data with multiple dimensions
        \item Support geographical and time-base queries
    \end{itemize}
\end{itemize}

>>>>

\section{Problem Statement}
Handling spatio-temporal weather data is challenging. Need an extendable system to support weather models by efficiently storing and retrieving data. Therefore, in this context the problem can be state as;
\emph{necessaty of a Data Integration System which is scalable, highly available and capable of 
interact with different data formats including spatio-temporal bulk stream data, 
store efficiently while optimizing the disk space,
support geographical and time-base queries,
third parties can access the data with easy integration, and
able to easy modify and use based on the requirements.
}

\section{Objectives}
We address above problem statement by achieving the following objectives:
\begin{itemize}
    \item To develop an open platform to integrate weather data from different sources in different formats
    \item To design and develop a schema to store multidimensional weather timeseries data while optimizing access time, availability, and storage
    \item To optimize schema to support data queries based on geography and time
    \item To develop an API to share data
    \item To use open source tools and provide the source publicly with appropriate liecense.
\end{itemize}
